Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/type-theory.tex
[ paper ] fixed typo.
[ paper ] type theory introcution improved.

Type theory is another formalism for the foundation of mathematics, and it has become in a key instrument to study logic and proof theory.
It was proposed in 1902 to avoid the Russell's paradox and it follows
the same philosophy of constructive mathematics where the witness of
a statement is \emph{everything}. In that direction, we could say
the main actors in type theory are the statements and their proofs.
By following the Curry-Howard correspondence, we say
\emph{types} are theorems and their \emph{terms} are their proofs.

Since the type theory is formal system, we have a syntax and a set of
derivation rules. These rules enables us to derive a kind of conclusions called
\emph{judgments}. A judgment is another way a term has certain type.

@@

We produce derivation trees inside the judgments using the derivation rules. The task to verify if a proof proves a certain theorem becomes in verify if the
derivation tree of the proof has the type of the theorem. This process is known
as type-checking. This feature of type theory allow us to verify a proof
generated by \ATPs by reconstructing its proof-term to type-check the proof.
However, type theory has some limitations for proof-reconstruction as we
describe in the following section.

>>>>

Type theory is another formalism for the foundation of mathematics, and it has became in a key instrument to study logic and proof theory.
It was proposed in 1902 to avoid the Russell's paradox and it follows
the same philosophy of constructive mathematics where the witness of
a statement is \emph{everything}. In that direction, we could say
the main actors in type theory are the statements and their proofs.
By following the Curry-Howard correspondence, we say
\emph{types} are theorems and their \emph{terms} are their proofs.

Since type theory is a formal system, we have a syntax and a set of
derivation rules. These rules enables us to derive a kind of conclusions called
\emph{judgments}. A judgment is another way to say a term has certain type.

@@

We produce derivation trees inside the judgments using the derivation rules.
Since type theory can be seen as typed lambda calculus with dependent products,
evaluation of lambda terms also called \emph{normalization} of the proofs-terms, are reductions using the system inference rules.

Therefore, the task to verify a proof that proves a certain theorem is
translated to verify if the associated tree of the proof has the correspondent
type of the theorem. This process is known as \emph{type-checking}. This feature
of type theory allow us to verify a proof generated by \ATPs by reconstructing
its proof-term to type- check the proof. However, type theory has some
limitations for proof- reconstruction as we describe in the following section.
